---
title: "DG"
author: "Matteo Ploner"
date: "`r format(Sys.time(), '%d %B, %Y')`"

output:

  prettydoc::html_pretty:
    theme: leonids #hpstr #tactile #hpstr
    highlight: github

  html_document:
    number_sections: true
    toc: true # table of content true
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    toc_float: true
    theme: cosmo  #united; paper; cerulean
    highlight: tango  # specifies the syntax highlighting style

  ioslides_presentation:
    toc: yes
    toc_depth: 2
    incremental: no
    smaller: no
    widescreen: yes
    duration: 90
    self_contained: yes

  slidy_presentation:
    footer: "FOOTER"
    duration: 90
    self_contained: yes

  beamer_presentation: default

  revealjs::revealjs_presentation:
    reveal_options:
      slideNumber: true
      previewLinks: false
      controls: false
      navigationMode: linear #grid, default
    theme: sky #“default”, “simple”, “sky”, “beige”, “serif”, “solarized”, “blood”, “moon”, “night”, “black”, “league” or “white”
    highlight: pygments
    slideNumber: true

  pdf_document:
    keep_tex: true
    number_sections: true
    df_print: kable
documentclass: article
fontsize: 11pt
geometry: margin=1in

#css: PATHto/.css
#bibliography: PATHto/.bib
---


# Sample  {.tabset .tabset-fade .tabset-pills}

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
library(tidyverse)
library(knitr)

setwd("/Users/matteo/Google Drive/WORK/insegnamento/VARIE/smart_BEEjS/lectures/2_soc_prefs/data")



```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=9, fig.align="center"}
library(tidyverse)

d <- full_join(
read_csv("./mod_DG_2020-06-18.csv"),
read_csv("./dict_KW_2020-06-18.csv"),
by=c("participant.code")
) %>% filter(session.code.y=="thk80gj6" )

# switch

switches <- d %>% select(participant.code,player.C_1.x,player.C_2.x,player.C_3.x,player.C_4.x,player.C_5.x,player.C_6.x,player.C_7.x,player.C_8.x,player.C_9.x,player.C_10.x,player.C_11.x) %>% gather("key","Value",2:12) %>%
mutate(key= as.integer(substr(key,10,11))) %>% group_by(participant.code) %>% filter(Value==2) %>% summarise_at("key",~min(.))

dt <- full_join(d %>% select(participant.code), switches, by=c("participant.code"))%>% replace_na(list(key=12))

dt <- dt %>% mutate(type=ifelse(key==12,"CP",
ifelse(key==1,"MM",
ifelse(key==11,"wS",
ifelse(key>=8 & key<11,"IA",
ifelse(key>5 & key<=7,"WE",
"AL"))))))
```

## Our Results: Individual behavior

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=9, fig.align="center"}
full_join(
d %>% select(participant.code,player.C_1.x,player.C_2.x,player.C_3.x,player.C_4.x,player.C_5.x,player.C_6.x,player.C_7.x,player.C_8.x,player.C_9.x,player.C_10.x,player.C_11.x) %>% gather("key","Value",2:12),
dt %>% select(-key), by=c("participant.code")) %>%
mutate(key= as.integer(substr(key,10,11))) %>%
ggplot(aes(x=key,y=Value,color=type))+
geom_line(size=2)+
theme_dark()+
facet_wrap(.~participant.code)+
scale_y_continuous(
  breaks = c(1,2),
  minor_breaks = c(1,2),
  labels = c("A","B")
)+
scale_x_continuous(
  breaks = 1:11,
  minor_breaks = 1:11
)

```

## Our Results: Distribution of Types

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=9, fig.align="center"}

dt %>% group_by(type) %>% count() %>% ungroup() %>% mutate(Freq=prop.table(n)) %>%
ggplot(aes(x=fct_reorder(type,desc(n)),y=n))+
geom_col(fill="dodgerblue",color="grey22",alpha=.6)+
 theme_bw() +
 labs(title="Types",
     subtitle="",
     y = "Freq",
     x= "Type",
     fill="",
     caption="SOURCE")+ # labels
theme(legend.position="bottom",
      axis.text=element_text(size=8),
      axis.title=element_text(size=14,face="bold"),
      axis.text.x = element_text(angle = 0, hjust = 1,vjust=0.5)) #axis
```

# Norms

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=7.5, fig.width=6, fig.align="center"}
#[[4, 'Very appropriate'],[3, 'Somewhat appropriate'],[2,'Somewhat inappropriate'],[1,'Very inappropriate']])
dt.g <- d %>% select(participant.code,player.C_1.y,player.C_2.y,player.C_3.y,player.C_4.y,player.C_5.y,player.C_6.y,player.C_7.y,player.C_8.y,player.C_9.y,player.C_10.y,player.C_11.y) %>% gather("key","Value",2:12) %>%
mutate(key= as.integer(substr(key,10,11))) %>%
group_by(key,Value) %>% count() %>% ungroup() %>% group_by(key) %>% mutate(freq=prop.table(n)) %>%
mutate(Value=ifelse(Value==4,'Very appropriate',ifelse(Value==3,'Somewhat appropriate',ifelse(Value==2,'Somewhat inappropriate','Very inappropriate'))))

dt.g$Value <- factor(dt.g$Value ,ordered = TRUE,
                                levels = c("Very inappropriate", "Somewhat inappropriate", "Somewhat appropriate", "Very appropriate") )


ggplot(dt.g,aes(x=Value,y=freq))+
geom_col(fill="dodgerblue")+
 theme_bw() +
 facet_wrap(.~key,ncol=1)+
 scale_y_continuous(breaks=c(0,.25,.5,.75))+
 labs(title="Social Appropriateness",
     subtitle="",
     y = "Freq",
     x= "Assessment",
     fill="")+ # labels
theme(legend.position="bottom",
      axis.text=element_text(size=8),
      axis.title=element_text(size=10,face="bold"),
      axis.text.x = element_text(angle = 45, hjust = 0,vjust=0)) #axis

```


```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}

full_join(
d %>% select(participant.code,player.C_1.y,player.C_2.y,player.C_3.y,player.C_4.y,player.C_5.y,player.C_6.y,player.C_7.y,player.C_8.y,player.C_9.y,player.C_10.y,player.C_11.y) %>% gather("Key","Value.Guess",2:12) %>% mutate(Key=substr(Key,10,11)),
d %>% select(participant.code,player.C_1.x,player.C_2.x,player.C_3.x,player.C_4.x,player.C_5.x,player.C_6.x,player.C_7.x,player.C_8.x,player.C_9.x,player.C_10.x,player.C_11.x) %>% gather("Key","Value.Choice",2:12) %>% mutate(Key=substr(Key,10,11)),
by=c("participant.code","Key")
) %>% group_by(Value.Choice) %>% summarise_at("Value.Guess",~mean(.)) %>%
mutate(Value.Choice=ifelse(Value.Choice==1,"A","B")) %>%
ggplot(aes(x=as.factor(Value.Choice),y=Value.Guess))+
geom_col(fill="dodgerblue")+
 theme_bw() +
 labs(title="",
     subtitle="",
     y = "Score of Social Appropriateness of A",
     x= "Choice",
     fill="")+ # labels
theme(legend.position="bottom",
      axis.text=element_text(size=8),
      axis.title=element_text(size=14,face="bold"),
      axis.text.x = element_text(angle = 90, hjust = 1,vjust=0.5)) #axis
```

- Which directions does causality run?
  - Norms &rarr; Behavior
  - or
  - Behavior &rarr;  Norms
