---
title: "Report Prolific"
author: "Matteo Ploner"
date: "`r format(Sys.time(), '%d %B, %Y')`"

output:

  prettydoc::html_pretty:
    theme: cayman #hpstr #tactile #hpstr
    highlight: github

  html_document:
    number_sections: true
    toc: true # table of content true
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    toc_float: true
    theme: cosmo  #united; paper; cerulean
    highlight: tango  # specifies the syntax highlighting style

  ioslides_presentation:
    toc: yes
    toc_depth: 2
    incremental: no
    smaller: no
    widescreen: yes
    duration: 90
    self_contained: yes

  slidy_presentation:
    footer: "FOOTER"
    duration: 90
    self_contained: yes

  beamer_presentation: default

  revealjs::revealjs_presentation:
    reveal_options:
      slideNumber: true
      previewLinks: false
      controls: false
      navigationMode: linear #grid, default
    theme: sky #“default”, “simple”, “sky”, “beige”, “serif”, “solarized”, “blood”, “moon”, “night”, “black”, “league” or “white”
    highlight: pygments
    slideNumber: true

  pdf_document:
    keep_tex: true
    number_sections: true
    df_print: kable
documentclass: article
fontsize: 11pt
geometry: margin=1in

#css: PATHto/.css
#bibliography: PATHto/.bib
---


# Sample  {.tabset .tabset-fade .tabset-pills}

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
library(tidyverse)
library(knitr)
library(kableExtra)
library(formattable)

setwd("/Users/matteo/Dropbox/SHARED/GuiltLegitimacy/esperimento_3/data")
# Prolific ID
d.p <- read_csv("prolific_id_2020-06-14.csv")
# Questionnaire
d.q <- read_csv("demo_questionnaire_2020-06-12.csv")

# Spectators
d.s <- left_join(
        left_join(
          read_csv("guilt_IS_2020-06-12.csv") %>% filter(participant._current_app_name=="prolific_end" & (session.code==	"wdi8mrbe" | session.code=="4kusmblf")),
          d.p %>% select(participant.code,player.prolific_id),
          by=c("participant.code")),
        d.q %>% select(participant.code, player.sex, player.age, player.comment, player.residence ), by=c("participant.code")
      ) %>% mutate(player.prolific_id=as.factor(player.prolific_id))

# Workers
d.w <- left_join(read_csv("guilt_W_2020-06-14.csv") %>% filter(participant._current_app_name=="prolific_end" & (session.code==	"gxycjgjn")),
d.p %>% select(participant.code,player.prolific_id),
by=c("participant.code"))

```

## Workers

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
d.w %>% select(player.type, participant.code,group.id_in_subsession,player.prolific_id) %>% distinct() %>% kable()
```

- One A is missing because some dropped out of the task


## Spectators

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
d.s %>% kable() %>%
  row_spec(0,background="black") %>%
kable_styling(font_size=12,full_width=T) %>%
scroll_box(height = "400px")
```

- Sessions: `r d.s %>% distinct(session.code) %>% nrow()`
`r d.s %>% distinct(session.code) %>% kable() %>% kable_styling()`
- Participants: `r d.s %>% distinct(participant.code) %>% nrow()`

- Participants per lambda

`r d.s %>% group_by(player.treatment) %>% count() %>% kable() %>% kable_styling()`

### Demographics

- Age

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
d.s %>% group_by(player.age) %>% count() %>% ungroup() %>% mutate(Freq=prop.table(n)) %>% arrange(desc(Freq)) %>% kable() %>% kable_styling()
```

- Gender

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
d.s %>% group_by(player.sex) %>% count() %>% ungroup() %>% mutate(Freq=prop.table(n)) %>% arrange(desc(Freq))%>% kable() %>% kable_styling()
```
- Country

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
d.s %>% group_by(player.residence) %>% count() %>% ungroup() %>% mutate(Freq=prop.table(n)) %>% arrange(desc(Freq))%>% kable() %>% kable_styling()

```

### Comments

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
d.s %>% select(player.comment) %>% na.omit() %>% kable() %>% kable_styling()
```

## Workers {.tabset .tabset-fade .tabset-pills}


# Spectators' choices {.tabset .tabset-fade .tabset-pills}

## Allocations {.tabset .tabset-fade .tabset-pills}

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=12, fig.align="center"}
#C: 1-> return; 0 -> Not return
# C_1: 0-25% expectation
# C_2: 26-50% expectation
# C_3: 51-75% expectation
# C_4: 76-100% expectation

d.s %>% select(participant.code,player.treatment,player.C_1,player.C_2,player.C_3,player.C_4) %>% gather("Key","Choice",3:6) %>% group_by(player.treatment,Key) %>% summarise_at("Choice",~mean(.,nar.rm=TRUE)) %>%
mutate(Key=ifelse(Key=="player.C_1","Bel_0/25",ifelse(Key=="player.C_2","Bel_26/50",ifelse(Key=="player.C_3","Bel_51/75","Bel_75/100")))) %>%
ggplot(aes(x=as.factor(Key),y=Choice))+
geom_col(fill="Lightblue",color="black")+
facet_wrap(.~player.treatment)+
 theme_bw() +
 labs(title="Choices of spectators",
     subtitle="",
     y = "Freq (rel)",
     x= "Worker B's Belief",
     fill="")+ # labels
theme(legend.position="bottom",
      axis.text=element_text(size=8),
      axis.title=element_text(size=14,face="bold"),
      axis.text.x = element_text(angle = 90, hjust = 1,vjust=0.5)) #axis
```

## Norms

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=12, fig.align="center"}
# KW: [[4, 'Very inappropriate'],[3, 'Somewhat inappropriate'],[2,'Somewhat appropriate'],[1,'Very appropriate']]
# KW_1: 0-25% expectation
# KW_2: 26-50% expectation
# KW_3: 51-75% expectation
# KW_4: 76-100% expectation

d.s %>% select(participant.code,player.treatment,player.KW_1,player.KW_2,player.KW_3,player.KW_4) %>% gather("Key","Choice",3:6) %>% mutate(Choice=ifelse(Choice==4,"Very inappropriate",ifelse(Choice==3,"Somewhat inappropriate",ifelse(Choice==2, "Somewhat appropriate","Very appropriate")))) %>% mutate(Choice=factor(Choice, levels = c("Very inappropriate", "Somewhat inappropriate", "Somewhat appropriate", "Very appropriate"))) %>%
mutate(Key=ifelse(Key=="player.KW_1","Bel_0/25",ifelse(Key=="player.KW_2","Bel_26/50",ifelse(Key=="player.KW_3","Bel_51/75","Bel_75/100"))))  %>% group_by(player.treatment,Key,Choice) %>% count() %>% ungroup() %>% group_by(Key,player.treatment) %>%
mutate(Freq=prop.table(n)) %>%
ggplot(aes(x=as.factor(Choice),y=Freq,fill=as.factor(Choice)))+
geom_col(color="black")+
facet_grid(Key~player.treatment)+
 theme_bw() +
 labs(title="Spectators' perceived norms",
     subtitle="",
     y = "Freq (rel)",
     x= "Norm",
     fill="")+ # labels
theme(legend.position="none",
      axis.text=element_text(size=8),
      axis.title=element_text(size=14,face="bold"),
      axis.text.x = element_text(angle = 90, hjust = 1,vjust=1.5)) #axis

```

# Payments

## Spectators

- At the end of the session, one of the four choices will be randomly selected for payment.
- For the randomly selected choice, the payment is computed as follows:
  - choices of all participants in the session who faced the same restoring probability you faced are counted, and the social appropriateness level chosen by the majority is computed;
    - if your choice <i>is</i> the same as that chosen by the majority, you earn an additional £0.5 (50p);
    - if your choice <i>is not</i> the same as that chosen by the majority, you earn £0. <p>

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
set.seed(1234)
rdm.choice <- sample(c("player.KW_1","player.KW_2","player.KW_3","player.KW_4"),1)
```

Randomly selected belief: `r rdm.choice`

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
d.pay <- full_join(
d.s %>% select(player.prolific_id,participant.code,player.treatment,player.KW_1,player.KW_2,player.KW_3,player.KW_4) %>% gather("Key","Choice",4:7),

# majority
d.s %>% select(player.prolific_id,participant.code,player.treatment,player.KW_1,player.KW_2,player.KW_3,player.KW_4) %>% gather("Key","Choice",4:7)  %>%
group_by(player.treatment,Key,Choice) %>% count() %>% ungroup %>% group_by(player.treatment,Key) %>% filter(n==max(n)) %>% rename(Majority_choice=Choice),
by=c("player.treatment","Key")
) %>%
mutate(Correct_bel=ifelse( Choice==Majority_choice,1,0))

# because we have some tie break
pay <- d.pay %>% filter( Key == rdm.choice ) %>% group_by(player.prolific_id) %>% summarise_at("Correct_bel",~sum(.)) %>% mutate(bonus_pay=ifelse(Correct_bel==1,.5,0)) %>% mutate(N=1:nrow(.)) %>% select(N,player.prolific_id,bonus_pay)

pay %>% kable() %>% kable_styling()
```

Spesa totale = `r pay %>% summarise_at("bonus_pay",~sum(.))`

## Workers

### Work

If he/she <b>does not return</b>, Worker A earns £12 and Worker B earns £0.</li>
<li>	If he/she <b>returns</b>, Worker A earns £9, but Worker B restores his/her reward of £7 only up to a certain restoring probability, that can range between 67% and 100%. The outcome of the restitution in this case is determined with a die roll performed by the computer. When Worker B does not restore his/her reward, the £7 reward is misplaced to an <i>Individual C</i>, who did not do any work. </li>


- partial groups (1,2)

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
payoffs <- tibble()
set.seed(4321)
# player.type participant.code group.id_in_subsession
# <chr>       <chr>                             <dbl>
# 1 C           3fbrtktv                              1
# 2 B           8sswryeq                              2
# 3 C           lfmeev60                              2

worker_belief <- d.w %>% filter(group.id_in_subsession==2 & player.type=="B" & subsession.round_number==7) %>% select(player.guess)
#1)randomly select a spectator and her choice, conditional upon worker B beliefs
# 1=return
spectator <- d.s %>% sample_n(1)
spectator.choice <- spectator %>% select(paste("player.C_",worker_belief,sep="")) %>% pull()
#2) define restore (according to type of spectator player.treatment)
#1=restore
restore <- ifelse(sample(1:6,1)<= spectator %>% select(player.treatment) %>% pull(),1,0)

#3) compute payoffs
#B
payoffs <- bind_rows(payoffs,
d.w %>% filter(player.type=="B" & (group.id_in_subsession==1 |group.id_in_subsession==2) ) %>% mutate(player.payoff=ifelse(spectator.choice==0,0,ifelse(restore==1,7,0))) %>% select(player.prolific_id,player.payoff) %>% distinct()
)
#C
payoffs <- bind_rows(payoffs,
d.w %>% filter(player.type=="C" & (group.id_in_subsession==1 | group.id_in_subsession==2) ) %>% mutate(player.payoff=ifelse(spectator.choice==0,0,ifelse(restore==1,0,7))) %>% select(player.prolific_id,player.payoff) %>% distinct()
)
```

- full group (3)

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
set.seed(1234)

# 4 A           ce58mxbj                              3
# 5 B           43pabo23                              3
# 6 C           08mfaoys                              3
#--------------------------------------
# group ==3
# all roles
#--------------------------------------
# # player.guess
# 1= 0-25%
# 2=25-50%
# 3=51-75%
# 4=76-100%
worker_belief <- d.w %>% filter(group.id_in_subsession==3 & player.type=="B" & subsession.round_number==7) %>% select(player.guess)
#1)randomly select a spectator and her choice, conditional upon worker B beliefs
# 1=return
spectator <- d.s %>% sample_n(1)
spectator.choice <- spectator %>% select(paste("player.C_",worker_belief,sep="")) %>% pull()
#2) define restore (according to type of spectator player.treatment)
#1=restore
restore <- ifelse(sample(1:6,1)<=spectator %>% select(player.treatment) %>% pull(),1,0)
#3) compute payoffs
#A
payoffs <- bind_rows(payoffs,
d.w %>% filter(player.type=="A" & group.id_in_subsession==3 ) %>% mutate(player.payoff=ifelse(spectator.choice==0,12,9)) %>% select(player.prolific_id,player.payoff) %>% distinct()
)
#B
payoffs <- bind_rows(payoffs,
d.w %>% filter(player.type=="B" & group.id_in_subsession==3 ) %>% mutate(player.payoff=ifelse(spectator.choice==0,0,ifelse(restore==1,7,0))) %>% select(player.prolific_id,player.payoff) %>% distinct()
)
#C
payoffs <- bind_rows(payoffs,
d.w %>% filter(player.type=="C" & group.id_in_subsession==3 ) %>% mutate(player.payoff=ifelse(spectator.choice==0,0,ifelse(restore==1,0,7))) %>% select(player.prolific_id,player.payoff) %>% distinct()
)

payoffs <- payoffs %>% rename(payoff.game=player.payoff)

```

### Beliefs

<p> To define your bonus payment, we will follow this procedure:</p>
<ol>
  <li>We will collect the return choices of all third persons, for all three levels of restoring probability. </li>
  <li> One return choice of the third person will be randomly drawn.</li>
  <li> The randomly drawn choice of the third person will be compared with your estimate.</li>
  <li> The matching between your estimate and the choice of the third person will define your earnings, as from the table below.</li>


```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}
# draw return choice conditional upon their beliefs

return.choice <- d.s %>% select(player.C_1,player.C_2,player.C_3,player.C_4) %>% gather("key","value",1:4)
#
workers <- d.w %>% select(player.type, participant.code,group.id_in_subsession,player.prolific_id) %>% distinct()

payoff_bel <- tibble()
for (i in workers$player.prolific_id){
   guess <- d.w %>% filter(subsession.round_number==7 & player.prolific_id==i) %>% select(player.guess) %>% pull()
   return <- sample_n(return.choice %>% filter(key==paste("player.C_",guess,sep="")),1)
   payoff_bel <- bind_rows(payoff_bel,
     d.w %>% filter(subsession.round_number==7 & player.prolific_id==i) %>% mutate(
     payoff = ifelse(guess==1,ifelse(return==0,.5,0),ifelse(guess==2,ifelse(return==0,.44,.28),ifelse(guess==3,ifelse(return==0,.28,.44),ifelse(return==0,0,.5))))) %>% select(player.prolific_id,payoff)
   )
}

payoff_bel <- payoff_bel %>% rename(payoff.bel= payoff)
```

### Total payoffs

Sum of beliefs and game

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align="center"}

full_join(payoffs, payoff_bel,by=c("player.prolific_id")) %>% mutate(payoff.TOT=payoff.bel + payoff.game)%>% kable() %>% kable_styling()
#
# <tr>
#   <th scope="row">Your earnings if a third person <i>chooses Return</i></th>
#   <td style="text-align:center">£0.00</td>
#   <td style="text-align:center">£0.28</td>
#   <td style="text-align:center">£0.44</td>
#   <td style="text-align:center">£0.50</td>
# </tr>
# <tr>
#   <th scope="row">Your earnings if a third person <i>does not choose  Return</i></th>
#   <td style="text-align:center">£0.50</td>
#   <td style="text-align:center">£0.44</td>
#   <td style="text-align:center">£0.28</td>
#   <td style="text-align:center">£0.00</td>



```

# Appendix
## Download the data

### Spectators

```{r echo=FALSE}
write_csv(d.s,"DATA_spectators.csv")

xfun::pkg_load2(c("base64enc", "htmltools", "mime"))
xfun::embed_file('./DATA_spectators.csv')
```

### Workers

```{r echo=FALSE}
write_csv(d.w,"DATA_workers.csv")

xfun::pkg_load2(c("base64enc", "htmltools", "mime"))
xfun::embed_file('./DATA_workers.csv')
```
